### 2021-05-05 thesis/tex/DCtheory.tex
update

\documentclass[draft=True]{revtex4-2}
\newcommand{\zreco}{\ensuremath{\cos{(\theta_z^{reco})}}}
\newcommand{\ztrue}{\ensuremath{\cos{(\theta_z^{true})}}}
\newcommand{\emm}{\ensuremath{\epsilon_{\mu\mu}}}
\newcommand{\emt}{\ensuremath{\epsilon_{\mu\tau}}}
\newcommand{\eet}{\epsilon_{e\tau}}
\newcommand{\eem}{\epsilon_{e\mu}}
\newcommand{\ett}{\ensuremath{\epsilon_{\tau\tau}}}
\newcommand{\ep}{\ensuremath{\epsilon^\prime}}
\renewcommand{\ne}{\nu_e}
\newcommand{\Ereco}{E^{reco}}
\newcommand{\Etrue}{E^{true}}
\newcommand{\nm}{\nu_\mu}
\newcommand{\nt}{\nu_\tau}
\newcommand{\ane}{\bar\nu_e}
\newcommand{\anm}{\bar\nu_\mu}
\newcommand{\ant}{\bar\nu_\tau}
\newcommand{\dm}{\Delta m^2_{31}}
\newcommand{\sth}{\sin^2(2\theta_{23})}

\usepackage{physics,amsmath, amsfonts, siunitx, amssymb, graphicx}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\begin{document}
\section{Methodology}
The neutrino flux at the detector is calculated by propagating the atmospheric neutrino flux~\cite{hondapaper} through the Earth by solving the 
Schrödinger equation for varying density. The Earth density profile is taken from the PREM~\cite{PREM}. The baseline for a given trajectory is determined using an average neutrino
production height of 15 km and an Earth radius of 6371 km. %TODO: add more here?

The oscillation probability $P_{\alpha \beta}$ acts as a weight to the atmospheric flux, yielding the propagated flux at detector level for flavor $\beta$ as 
\begin{align}\label{eq:propFlux}
    \phi_\beta^\text{det} = \sum_\alpha P_{\alpha\beta} \phi_\alpha^\text{atm} \,,
\end{align}
where we sum over the initial lepton flavors $\alpha \in \{e,\mu, \bar{e}, \bar{\mu}\}$. To illustrate the impact of $\emt$ on both probability
and flux level, we plot the oscillograms resulting from Eq.\ref{eq:propFlux} in Fig.~\ref{fig:flux_ratio}. In the left panel, we have marked the region in which 99\% of the 
DeepCore cascade events originating from $\ne$ and $\nt$ fluxes are contained. In the right panel, we show the two regions in which 99\% of the IceCube 
and DeepCore track events originating from $\nm$ fluxes are contained. Starting with the $\nm$ flux ratio, we see that the only clear signal discernible to the IceCube detector
is a flux deficiency of a factor of $\sim 10^2$ from core-crossing neutrinos within a zenith range of $\ztrue > -0.87$. DeepCore, on the other hand, 
observes multiple fringes of flux surpluses with a factor $\sim 10^1$. The strongest surplus at \SI{20}{\GeV} is very weakly zenith dependent, a stark contrast to the
energy-independent but zenith-sensetive IceCube deficiency.

For the fluxes which drives cascades, we have to resort to the DeepCore detector alone. %TODO: fill more
Here we see a somewhat weaker signal, this time a zenith-independent deficiency. 
%TODO: fill with conclusion

\begin{figure}[!tb]
   \begin{center}
      \includegraphics[width=0.4\linewidth]{figures/cascade_flux_ratio.pdf}
      \hspace{1.5cm}
      \includegraphics[width=0.4\linewidth]{figures/track_flux_ratio.pdf}
   \end{center}
   \caption{Ratio of propagated NSI to SI atmospheric fluxes at detector level. We set $\emt = -0.05$, and all other NSI parameters to zero. 
   Dotted (dashed) lines show the regions in which 99\% of the 
   DeepCore (IceCube) MC events are contained. \emph{Left panel:} Propagated fluxes of $\ne$ and $\nt$ neutrinos and anti-neutrinos. 
   \emph{Right panel:} Propagated fluxes of $\nm$ neutrinos and anti-neutrinos}\label{fig:flux_ratio}%TODO: normalize color scale and fix limits
\end{figure}

\subsection{IceCube}\label{ch:ICmethod}
The event rate for each bin reads
\begin{align}\label{eq:ICevents}
    N_{ij} &= T \int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r \int_0^\pi R(\theta^r,\theta^t) \dd \cos{\theta^t} \int_0^\infty R(E^r,E^t) \dd E^t
    \times \left[ \sum_\beta \phi_\beta^\text{det}  A^\text{eff}_\beta\right]\,,
\end{align}
where $T$ is the live time of the detector, and $A^\text{eff}_\beta$ its effective area for flavor $\beta$. We use the effective area of the 86 string configuration made public by the IceCube collaboration~\cite{ICaeff}. $R(x^r,x^t)$ is a resolution function, 
which is responsible for the smearing between the reconstructed and true parameters $x^r$ and $x^t$, respectively. We assume a log-normal distribution, giving it the form 
\begin{align}
    R(x^r, x^t) = \frac{1}{\sqrt{2\pi} \sigma_{x^r}x^r} \exp\left[-\frac{(\log x^r-\mu(x^t))^2}{2\sigma_{x^r}^2}\right]\,.
\end{align}
As seen in Fig.~\ref{fig:IC_MC_counts}, the energy reconstruction is biased. To model this relationship between $\Etrue$ and $\Ereco$, we train a Gaussian process regressor on the dataset~\cite{IC2016}, from which
we can extract a predicted mean and standard deviation for a given $E^{reco}$. We then take the $\Etrue$ points of the 99th percentile of each distribution to obtain
the limits of $\Etrue$ at which to integrate over. We have no angular resolution function since the angle resolution in Icecube for track-like events is less than $\SI{2}{\degree}$, making $\ztrue$ coincide with $\zreco$ for our study~\cite{IC2020}. 
The data is from the IC86 sterile analysis~\cite{IC2020}.
\begin{figure}[!tb]
    \begin{center}
       \includegraphics[width=0.4\linewidth]{figures/IC_MC_gpr.pdf} %TODO: another fig here? Aeff?
    \end{center}
    \caption{Relationship between the true and reconstructed muon energy in the IceCube MC sample~\cite{IC2016}}\label{fig:IC_MC_counts}. Shaded area shows the $99.9$th percentile limits predicted by the regressor trained on this set.
 \end{figure}

\subsection{DeepCore}\label{ch:DCmethod}
In this part, we use the publically available DeepCore data sample~\cite{DC2019data} which is an updated version of what was used by the 
IceCube collaboration in a $\nu_\mu$ disapprearance analysis~\cite{DC2018mudisappearance}.

@@

We plot the event pull $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ where $N_{(N)SI}$ are the numbers of expected events
assuming (non-)standard interactions in Fig.~\ref{fig:event_pulls}. This gives the normalized difference in the
number of expected events at the detector, and illustrates the expected sensitivity of DeepCore for the NSI parameters.

\begin{figure}[!tb]
   \begin{center}
      \includegraphics[width=0.7\linewidth]{figures/DC_event_pulls.pdf}
      \includegraphics[width=0.7\linewidth]{figures/PINGU_event_pulls.pdf}
   \end{center}
   \caption{Expected pulls of predicted event numbers for DeepCore and PINGU after 3 years. We compare the NSI event count with $\emt=-0.05$
    to the standard interaction count}\label{fig:event_pulls} %TODO: remake these with clearer titles and better labels
\end{figure}

\subsection{PINGU}\label{ch:PINGUmethod}
The methodology behind the PINGU simulations are the same as with our DeepCore study~\ref{ch:DCmethod}. We use the public MC~\cite{PINGUdata}, which allows us to construct the event count as in Eq.~\ref{eq:MCevents}.
However, since no detector systematics is yet modelled for PINGU, the correction factors $C_{ijk}$ are all unity.
As with the DeepCore data, the PINGU MC is divided into eight 
$\log_{10}E^{reco} \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins for both track- and cascade-like events. 
We generate "data" by predicting the event rates at PINGU with the following best-fit parameters from~\cite{nufit}, except for the CP-violating phase which is set to zero for simplicity.

\begin{align}\label{eq:PINGUparams}
    &\Delta m^2_{21} =  \SI{7.42e-5}{\electronvolt^2},\hspace{0.5em} \dm =  \SI{2.517e-3}{\electronvolt^2}, \nonumber \\
    &\theta_{12} = \SI{33.44}{\degree},\hspace{1em} \theta_{13} = \SI{8.57}{\degree},\hspace{1em} \theta_{23} = \SI{49.2}{\degree}, \hspace{1em} \delta_\text{CP} = 0\,.
\end{align}

\section{Results}
For our analyses, we define our $\chi^2$ as
\begin{align} \label{eq:ICchisq}
    \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
    {\left(\sigma^\text{data}_{ijk}\right)^{2} + \left(\sigma^\text{syst}_{ijk}\right)^{2}}+ 
    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
\end{align}
where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \ep, \emt\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
$N_{ijk}^\text{th}$ is the expected number of events from theory, and $N_{ijk}^\text{data}$ is the observed number of events in that bin. We set $\sigma_\alpha = 0.25$ as the atmospheric flux normalization error, and $\sigma_\beta = 0.04$ as the zenith angle slope error~\cite{hondapaper}. 
The observed event number has an associated Poissonian uncertainty $\sigma_{ijk}^\text{data} = \sqrt{N_{ijk}^\text{data}}$.

For IceCube, the event count takes the form
\begin{align}
    N^\text{th}_{ijk} = \alpha\left[1+\beta (0.5 + \zreco_i )\right] N_{ijk}(\hat{\theta})\,,
\end{align}
with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:ICevents} Here, we allow the event distribution to rotate around the median zenith of $-0.5$.

For DeepCore and PINGU, the event count takes the form
\begin{align}
    N^\text{th}_{ijk} = \alpha\left[1+\beta \zreco_i \right] N_{ijk}(\hat{\theta}) + \kappa N_{ijk}^{\mu_{atm}}\,,
\end{align}
with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:MCevents}. $N_{ijk}^{\mu_{atm}}$ is the muon background, which is left to float freely in the DeepCore analysis.
The background at PINGU can be considered neglible to first order~\cite{PINGUdata}, and we thus put $\kappa=0$ when calculating the PINGU $\chi^2$\,.
For IceCube, we set $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$.
For DeepCore, we use the provided systematic error distribution which accounts for both uncertanties in the finite MC statistics and in the data-driven 
muon background estimate~\cite{DC2019data}.

First, we set all standard oscillation parameters to their current best-fit values of Eq.~\ref{eq:PINGUparams}, except for $\dm$ and $\theta_{23}$, 
which we marginalize over their $3\sigma$ ranges of \SI{2.435e-3} to \SI{2.598e-3}{\electronvolt^2} and \SI{40.1} to \SI{51.7}{\degree} respectively. %TODO: make unit ranges nicer.

 \begin{figure}[!tb]
    \begin{center}
       \includegraphics[width=0.45\linewidth]{figures/PINGU_3D_ett.pdf}
       \includegraphics[width=0.45\linewidth]{figures/PINGU_3D_emt.pdf}
       \includegraphics[width=0.45\linewidth]{figures/PINGU_3D_eem.pdf}
       \includegraphics[width=0.45\linewidth]{figures/PINGU_3D_eet.pdf}
    \end{center}
    \caption{The expected values of $\Delta \chi^2$ after three years of PINGU data. $\dm$ and $\theta_{23}$ and have been marginalized out, and all NSI 
    parameters not shown in each plot are set to zero.}\label{fig:PINGU_3D}
 \end{figure}

 \begin{figure}[!tb]
    \begin{center}
       \includegraphics[width=0.4\linewidth]{figures/DC_emm.pdf}
       \includegraphics[width=0.4\linewidth]{figures/DC_emt.pdf}
    \end{center}
    \caption{The expected values of $\Delta \chi^2$ after three years of PINGU data. $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
    parameters are set to zero. The black lines show the 90\% credibility region from~\cite{demidov}}\label{fig:DC_3D_et}
 \end{figure}

For the joint analysis, we follow the parameter goodness-of-fit prescription~\cite{maltoni2003} and construct the joint $\chi^2$ as 
\begin{align}
    \chi^2_\text{joint} = \chi^2_\text{IC} + \chi^2_\text{DC} + \chi^2_\text{P} - \chi^2_{IC,min} - \chi^2_\text{DC,min} - \chi^2_\text{P,min}\,
\end{align}
with test statistic $\chi^2_\text{joint,min}$.

\begin{figure}[!tb]
    \begin{center}
       \includegraphics[width=0.4\linewidth]{figures/emm_deltachi.pdf}
    \end{center}
    \caption{}\label{fig:emm_deltachi}
 \end{figure}

 \begin{figure}[!tb]
    \begin{center}
       \includegraphics[width=0.4\linewidth]{figures/emm_emp_contour.pdf}
    \end{center}
    \caption{}\label{fig:emm_emp_contour}
 \end{figure}
%At $90\%$ CL:
%PINGU: $-0.046 < \emm < 0.041$
%DC: $-0.045 < \emm < 0.041$
%joint: $-0.038 < \emm < 0.033$

%TODO: table with individual and combined chisq values. Discussion on impact of IC on chisq.

 \newpage
\begin{tabular}{p{55mm}p{55mm}p{55mm}}
   DeepCore (2017)
      \begin{itemize}
         \item[$\checkmark$] Honda atmospheric fluxes
         \item[$\times$] Only look at tracks and $\emt$
         \vspace{1em}  
         \item[$\times$] DC Monte Carlo from an older dataset 
         \item[$\times$] 8 E bins from $\SI{6.3}{\electronvolt^2}$ to $\SI{56}{\electronvolt^2}$
         \item[$\times$] 8 z bins from -1 to 0 
         \item[$\times$] Use "Overall" and "relative $\ne$ to $\nm$" normalization
         \item[$\times$] Prior on spectral index
         \item[$\times$] No zenith angle normalization
         \item[$\checkmark$] No priors on $\dm, \theta_{23},\theta_{13}$
      \end{itemize} &
    Demidov (2020) DC analysis
      \begin{itemize}
         \item[$\checkmark$] Honda atmospheric fluxes
         \item[$\checkmark$] Looks at tracks + cascades for $\emt$ and $\ett$
         \item[$\checkmark$] Data and Monte Carlo from DC 2018
         \item[$\checkmark$] 8 E bins from $\SI{5.6}{\electronvolt^2}   $ to $\SI{56}{\electronvolt^2}$
         \item[$\checkmark$] 8 z bins from -1 to 1
         \item[$\times$] Use "Overall" and "relative $\ne$ to $\nm$" normalization
         \item[$\times$] Prior on spectral index
         \item[$\times$] No zenith angle normalization
         \item[$\checkmark$] No priors on $\dm, \theta_{23}$
         \item[$\checkmark$] Fixes $\Delta m^2_{21}, \theta_{12}, \theta_{13}$
         \item[$\times$] Uncertainty on hadron production in atmosphere
         \item[$\times$] Uncertainty on neutrino nucleon cross section 
      \end{itemize} &
    This DC+PINGU analysis
      \begin{itemize}
         \item[$\checkmark$] Honda atmospheric fluxes
         \item[$\checkmark$] Tracks and cascades for all flavors
         \vspace{1em} 
         \item[$\checkmark$] Reco $\to$ true mapping from Monte Carlo migration matrix
         \item[$\checkmark$] 8 E bins from $\SI{5.6}{\electronvolt^2}$ to $\SI{56}{\electronvolt^2}$
         \item[$\checkmark$] 8 zenith angle bins from -1 to 1
         \item[$\checkmark$] Flux normalization uncertainty of 25\%
         \item[$\checkmark$] Zenith angle uncertainty of 4\% 
         \item[$\checkmark$] No priors on oscillation parameters 
         \item[$\checkmark$] Marginalize $\dm$ and $\theta_{23}$. All other oscillation parameters are fixed.
      \end{itemize} 
\end{tabular}

\begin{table}
   \begin{center}
   \begin{tabular}{lcccc}
           \hline \hline & \multicolumn{3}{c} {\text {Best fit}}& \\
           \cline { 2 - 4 } Parameter & $\dm$ & $\theta_{23}$  & $\epsilon$ & 90\% CL of $\epsilon$ \\
           \hline
           $\ett$ &-& - & - & -\\
           $\emt$ &0.002435& 0.76736 & -0.005 & -0.015, 0.005\\
           $\eem$ &-& - & - & -\\
           $\eet$ &0.002435 & 0.7673630944601736 & 0.05 & -0.072, 0.138\\
           \hline
       \label{table:results}
   \end{tabular}
   \end{center}
   \caption{DeepCore results}
\end{table}

\begin{table}
   \begin{center}
   \begin{tabular}{lcccc}
           \hline \hline & \multicolumn{3}{c} {\text {Best fit}}& \\
           \cline { 2 - 4 } Parameter & $\dm$ & $\theta_{23}$  & $\epsilon$ & 90\% CL of $\epsilon$ \\
           \hline
           $\ett$ &-& - & - & -\\
           $\emt$ &-& - & - & -\\
           $\eem$ &-& - & - & -\\
           $\eet$ &0.002517 & 0.8587019919812102 & 0.05 & -0.105, 0.101\\
           \hline
       \label{table:results}
   \end{tabular}
   \end{center}
   \caption{DeepCore results}
\end{table}

\bibliographystyle{elsarticle-num}
\bibliography{article}
\end{document}

>>>>

\documentclass[draft=True]{thesis}
\usepackage[margin=0.5in]{geometry}
\usepackage{graphicx, slashed, siunitx}
\usepackage[utf8]{inputenc}
\usepackage{xr-hyper}
\input{commands}
\begin{document}
\section{DeepCore}
In this part, we use the publically available DeepCore data sample~\cite{DC2019data} which is an updated version of what was used by the 
IceCube collaboration in a $\nu_\mu$ disapprearance analysis~\cite{DC2018mudisappearance}.

@@

We plot the event pull $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ where $N_{(N)SI}$ are the numbers of expected events
assuming (non-)standard interactions in Fig.~\ref{fig:event_pulls}. This gives the normalized difference in the
number of expected events at the detector, and illustrates the expected sensitivity of DeepCore for the NSI parameters.
\section{PINGU}
The methodology behind the PINGU simulations are the same as with our DeepCore study~\ref{ch:DCmethod}. We use the public MC~\cite{PINGUdata}, which allows us to construct the event count as in Eq.~\ref{eq:MCevents}.
However, since no detector systematics is yet modelled for PINGU, the correction factors $C_{ijk}$ are all unity.
As with the DeepCore data, the PINGU MC is divided into eight 
$\log_{10}E^{reco} \in [0.75,1.75]$ bins, and eight $\zreco \in [-1,1]$ bins for both track- and cascade-like events. 
We generate "data" by predicting the event rates at PINGU with the following best-fit parameters from~\cite{nufit}, except for the CP-violating phase which is set to zero for simplicity.

\begin{align}\label{eq:PINGUparams}
    &\Delta m^2_{21} =  \SI{7.42e-5}{\electronvolt^2},\hspace{0.5em} \dm =  \SI{2.517e-3}{\electronvolt^2}, \nonumber \\
    &\theta_{12} = \SI{33.44}{\degree},\hspace{1em} \theta_{13} = \SI{8.57}{\degree},\hspace{1em} \theta_{23} = \SI{49.2}{\degree}, \hspace{1em} \delta_\text{CP} = 0\,.
\end{align}
\bibliographystyle{nature}
\bibliography{ref.bib}
\end{document}

### 2021-05-05 thesis/tex/ICintro.tex
update

\documentclass[draft=True]{thesis}
\usepackage{graphicx, slashed, siunitx}
\usepackage[utf8]{inputenc}
\usepackage{xr-hyper}
\input{commands}
\begin{document}
We always observe neutrinos indirectly through their associated charged lepton. Regardless of the type of interaction (charged current via the $W$ boson, or neutral current
via the $Z$), a charged lepton exits with altered properties. The lepton is then detected, and the properties of the neutrino involved in the 
interaction is then deduced. This deduction is obviously imperfect, and this introduces complexities that we will handle in Ch.~\ref{ch:ICmethod}.

In this work, we only study the detectors handeled by the ICecube collaboration. They are of Cherenkov type, which means that they detect 
the charged lepton by its emitted Cherenkov light, produced from its travel through the Antarctic ice. 
%TODO: text about pid
\begin{figure}\label{fig:events}
    \includegraphics[width=0.5\textwidth]{figures/cascade_event.pdf}\caption{Event classified as cascade}
    \includegraphics[width=0.5\textwidth]{figures/track_event.pdf}\caption{Event classified as track}
\end{figure}

@@

In 2017, the PINGU Letter of Intent was published~\cite{PINGUletter}. The "Precision IceCube Next Generation Upgrade" is an upgrade that will 
supplement DeepCore, i.e. boosing the capabilites of neutrino detection at the \si{\GeV} scale. As the PINGU upgrade is not yet financed nor built, we are
not able to use any data from it. However, the collaboration has released preliminary simulations which we will use to see how the upgrade might improve
IceCube and DeepCore bounds. 
\bibliographystyle{nature}
\bibliography{ref.bib}
\end{document}

>>>>

\documentclass{thesis}
\usepackage[margin=0.5in]{geometry}
\usepackage{graphicx, slashed, siunitx, subcaption}
\usepackage[utf8]{inputenc}
\usepackage{xr-hyper}
\input{commands}
\begin{document}
\section{Neutrino detection}
We always observe neutrinos indirectly through their associated charged lepton. Regardless of the type of interaction (charged current via the $W$ boson, or neutral current
via the $Z$), a charged lepton exits with altered properties. The lepton is then detected, and the properties of the neutrino involved in the 
interaction is then deduced. This deduction is obviously imperfect, and this introduces complexities that we will handle in Ch.~\ref{ch:ICmethod}.

In this work, we only study the detectors handeled by the IceCube collaboration. They are of Cherenkov type, which means that they detect 
the secondary charged lepton by its emitted Cherenkov light, produced from its travel through the Antarctic ice.

If the charged leptons interact heavily with the ice, they will travel a short distance and emit a localized flash of 
Cherenkov light. This event is referred to as a cascade. The neutral current interactions involves quarks, which recoils and procudes
showers of hadrons. Also, charged current $\ne$ interactions also produce cascades. A cascade event 
is shown in Fig.~\ref{fig:events_cascade}.

If the charged leptons don't interact as much in the ice, they penetrate a larger part of it, emitting light and tertiary particles
as they go. This event is referred to as a track, and are often due to muon charged current interactions. A track event 
is shown in Fig.~\ref{fig:events_track}.

\begin{figure}\label{fig:events}
    \begin{center}
        \begin{subfigure}{0.4\textwidth}
            \centering
            \includegraphics[clip, trim=0cm 0cm 0cm 30cm, width=1\textwidth]{figures/cascade_event.pdf}
            \caption{Event classified as cascade}  
            \label{fig:events_cascade}
          \end{subfigure}
        \begin{subfigure}{0.4\textwidth}
            \centering
            \includegraphics[clip, trim=0cm 0cm 0cm 30cm, width=1\textwidth]{figures/track_event.pdf}
            \caption{Event classified as track} 
            \label{fig:events_track}
        \end{subfigure}
        \caption{The two event types distinguished in the IceCube detector.}
    \end{center}
\end{figure}

@@

In 2017, the PINGU Letter of Intent was published~\cite{PINGUletter}. The "Precision IceCube Next Generation Upgrade" is an upgrade that will 
supplement DeepCore, i.e. boosing the capabilites of neutrino detection at the \si{\GeV} scale. As the PINGU upgrade is not yet financed nor built, we are
not able to use any data from it. However, the collaboration has released preliminary simulations which we will use to see how the upgrade might improve
IceCube and DeepCore bounds. The PINGU simulations have the same structure as the DeepCore data, so any analysis referring to DeepCore will
also apply to PINGU except where noted. However, we treat the PINGU detector as independent of the DeepCore experiment.
\bibliographystyle{nature}
\bibliography{ref.bib}
\end{document}

### 2021-05-05 thesis/tex/ICtheory.tex
update

\section{Atmospheric neutrino flux}
The flux comes from \cite{hondaArticle} %TODO: talk about flux
The flux data is binned in $\ztrue$ and a selection is shown in Table~\ref{table:flux}. The fluxes are averaged over azimuthal direction and over solar minimum/maximum. 
The units of the fluxes are given as \si{\per\GeV \per\metre\squared \per\second \per\steradian} and are omitted
from the table for clarity. 
We note that the fluxes for $\nt$ and $\nu_{\bar{\tau}}$ are missing. This is due to the rapid decay (and hence, low flux) of the $\tau$. 
Thus, we never have to use probabilities on the form 
$P_{\tau \beta}$, since we have no incoming atmospheric $\nu_\tau$ flux.

@@

\begin{figure}[!tb]\label{fig:IC_MC_gpr}
    \begin{center}
       \includegraphics[width=0.4\linewidth]{figures/IC_MC_gpr.pdf} %TODO: another fig here? Aeff?
    \end{center}
    \caption{Relationship between the true and reconstructed muon energy in the IceCube MC sample~\cite{IC2016}}\label{fig:IC_MC_counts}. Shaded area shows the $99.9$th percentile limits predicted by the regressor trained on this set.
 \end{figure}
\bibliographystyle{nature}
\bibliography{ref.bib}
\end{document}

>>>>

\section{Atmospheric neutrino flux}
Atmospheric neutrinos originates from cosmic rays composed of protons interacting with nuclei in the atmosphere.
These interactions ultimately produces pions, which decay as 
\begin{align}\label{eq:pion}
    \pi^+ &\to \mu^+ + \nm\,, \quad \pi^- \ to \mu^- + \anm \nonumber \\
    \pi^+ &\to e^+ + \ne\,, \quad \pi^- \ to e^- + \ane\,.
\end{align}
In the muonic decay channel, muons are emitted which will be detected by the IceCube detector. A part of the 
uncorrelated systematic error comes from this \emph{muon background}, i.e. events misclassified as muons from 
$\nm$ interactions rather than from pion decay. Moreover, the atmospheric flux is often associated with a large error.
In this work, we will use a flux normalization error of 24\%, and a zenith slope error of 4\%. In more sophisticated 
models, one can also include the pion to kaon flux uncertainty.

The flux is provided in \cite{hondaData,hondaArticle}, and a selection is shown in Table~\ref{table:flux}
The flux data is binned in $\ztrue$. The fluxes are averaged over azimuthal direction and over solar minimum/maximum. 
The units of the fluxes are given as \si{\per\GeV \per\metre\squared \per\second \per\steradian} and are omitted
from the table for clarity. 
We note that the fluxes for $\nt$ and $\nu_{\bar{\tau}}$ are missing. Kaons can decay into neutral pions, which in turn 
can produce $\nt$, but this branching ratio is extremely small. Thus, we never have to use probabilities on the form 
$P_{\tau \beta}$, since we have no incoming atmospheric $\nu_\tau$ flux.

@@

\begin{figure}[!tb]\label{fig:IC_MC_gpr}
    \begin{center}
       \includegraphics[width=0.4\linewidth]{figures/IC_MC_gpr.pdf}
    \end{center}
    \caption{Relationship between the true and reconstructed muon energy in the IceCube MC sample~\cite{IC2016}}\label{fig:IC_MC_counts}. Shaded area shows the $99.9$th percentile limits predicted by the regressor trained on this set.
 \end{figure}
\bibliographystyle{nature}
\bibliography{ref.bib}
\end{document}
